Slowest RS dynamics
========================================================

Here we try to find slowest (or bunch of slowest regionservers and look into their response change over time). I haven't used all available data, only two-three days, not more.

```{r}
source ("probe_io.R")
library(plyr)
```

```{r}
from_date <- as.POSIXct("2014-07-21")
to_date <- as.POSIXct("2014-08-05")
```

Data range for analisys `r from_date` -- `r to_date`, load it:
```{r}
  # add one day to upper bound
  to_date <- to_date + 24*60*60
  files <- c()  
  for (file in list.files("data", full.names=T)) {
    d <- probe_date(file)
    if (d >= from_date && d <= to_date) {
      files <- append(files, file)
    }
  }

  str(files)
```

Get slowest regionservers on first probe (file `r files[1]`)

```{r}
read_rs_mean_ord <- function(fname) {
  first <- read_probe(fname, semicolon=T)
  first_rs_mean <- ddply(first, .(RS), summarise, time=mean(Time))
  first_rs_mean[order(first_rs_mean$time, decreasing=T),]
}

ord_first <- read_rs_mean_ord(files[1])
head(ord_first, n=20)
plot(ord_first$time, type='l')
```

Get list of slowest regionservers over time
```{r}
slow_rses_over_time <- NULL
rs_times <- NULL

for (file in files) {
  ord <- read_rs_mean_ord(file)
  date <- probe_date(file)
  slow_rses_over_time <- rbind(slow_rses_over_time,
                               data.frame(date=date, rs=ord[1,]$RS, time=ord[1,]$time))
  rs_times <- rbind(rs_times,
                    cbind(date=date, ord))
}

head(slow_rses_over_time)
```

Hmm, in slowest list we have lots of the same regionservers:
```{r}
rses_count <- ddply(slow_rses_over_time, .(rs), summarise, count=length(rs))
rses_count <- rses_count[order(rses_count$count, decreasing=T),]
head(rses_count)
```

So, it's clear that slowest RS are not random, let's look on their benchmark over time.

```{r}
# take first and second most frequent slow rs regionservers
rs_1 <- rses_count$rs[1]
rs_2 <- rses_count$rs[2]
# take one RS which haven't been in slowest
rs_ok <- setdiff(rs_times$RS, rses_count$rs)[2]
plot(rs_times[rs_times$RS == rs_1, c('date', 'time')], type='l', col='red')
lines(rs_times[rs_times$RS == rs_2, c('date', 'time')], type='l', col='blue')
lines(rs_times[rs_times$RS == rs_ok, c('date', 'time')], type='l', col='black')

```

It looks like an effect caused by lack of compaction.