Test of probe reading
======================
This document is an example and test code for probe reading. Normally, it will read one probe sample, which consists from list of regions with their regionserver and probe time.

```{r}
source ("probe_io.R")
library(plyr)
```

This code reads probe data into data frame
```{r cache=TRUE}
df <- read_probe("data/2014-08-07_02.txt")
summary(df)
str(df)
```

Group reply time by regionserver and average
```{r}
d <- ddply(df, .(RS), summarise, time=mean(Time), count=length(Time))
# order by mean time
od <- d[order(d$time, decreasing=T),]
head(od, n=20)
```

Plots of regions in top-10 regionservers
```{r}
for (i in seq(10)) {
  a <- df[df$RS == od[i, "RS"],]
  plot(a$Time, type='l', main=od[i, "RS"])
}
```


Group reply time by regionserver and max
```{r}
dm <- ddply(df, .(RS), summarise, time=max(Time), count=length(Time))
odm <- dm[order(dm$time, decreasing=T),]
head(odm, n=20)
```

Top-20 regions by time
```{r}
odf <- df[order(df$Time, decreasing=T),]
head(odf, n=20)
```

Optimization
---------------------
Initial implementation of read_probe is not too great.

    system.time(df <- read_probe("data/2014-08-07_02.txt"))
     user  system elapsed 
     3.42    0.00    3.41 

The source of slowdown is the need to parse line-by-line. After switch to tab-separated format:

    system.time(df2 <- read_probe_tabs("data/2014-08-07_02-tabs.txt"))
     user  system elapsed 
     0.276   0.000   0.272